---
title: "EVS 2017 Data Exploration & Analysis"
output: html_document 
params:
  country: "All"
  outcome: "GenRol"
  controls: NULL
  poly_degree: 1
  reg_plot_path: NULL
  exp_plot_path: NULL
  reg_table_path: NULL
---
```{r setup, include=FALSE}
library(knitr)
library(pander)
library(readr)
library(RColorBrewer)
```

# Report for `r params$country`

## Variables Chosen

#### Selected Outcome Variable
`r ifelse(params$outcome == "GenRol", "Attitudes towards Traditional Gender Roles", "Attitudes towards Immigration")`

#### Control Variables
`r if (length(params$controls) > 0) paste(ifelse(params$controls == "Edu", "Education", params$controls), collapse = ", ") else "None"`

#### Polynomial Degree for Age
`r params$poly_degree`


## Graphs

```{r, echo=FALSE}
knitr::include_graphics(params$exp_plot_path)
```

```{r, echo=FALSE}
knitr::include_graphics(params$reg_plot_path) 
```


## Regression Table

```{r, echo=FALSE}
reg_table <- read.csv(params$reg_table_path) 
reg_table <- reg_table %>% 
  dplyr::mutate(across(
        where(is.numeric), 
        ~ ifelse(round(., 4) == 0, "<0.0001", format(round(., 4), nsmall = 4))
      )) %>%
      dplyr::mutate(term = case_when(
        grepl("poly\\(Age, [0-9]+\\)1", term) ~ "Age",
        grepl("poly\\(Age, [0-9]+\\)2", term) ~ "Age\u00B2",
        grepl("poly\\(Age, [0-9]+\\)3", term) ~ "Age\u00B3", 
        grepl("poly\\(Age, [0-9]+\\)4", term) ~ "Age\u2074", 
        grepl("poly\\(Age, [0-9]+\\)5", term) ~ "Age\u2075",
        TRUE ~ term
      )) %>%
      dplyr::rename(
        Term = term,
        `Reg Coef` = estimate,
        `SE` = std.error,
        `t-Statistic` = statistic,
        `p-Value` = p.value
      )
pander(reg_table,
    caption = "Data: EVS 2017.")
```

#### For more information, please access the GitHub Repository [here](https://github.com/rpengling/SURV675_Final.git)

